Flabby and injective objects in toposes

### 2022-02-14 paper-flabby-objects.tex
Acknowledge Verona

\textbf{Acknowledgments.} We are grateful to Thorsten Altenkirch, Simon Henry
and Maria Emilia Maietti for insightful discussions and pointers to prior work,
to Jürgen Jost, Marc Nieper-Wißkirchen and Peter Schuster for valuable
guidance, and to Daniel Albert and Caterina Cozzi for their careful readings of
earlier drafts. Most of the work for this note was carried out at the University of
Augsburg and the Max Planck Institute for Mathematics in the Sciences in
Leipzig.

>>>>

\textbf{Acknowledgments.} We are grateful to Thorsten Altenkirch, Simon Henry
and Maria Emilia Maietti for insightful discussions and pointers to prior work,
to Jürgen Jost, Marc Nieper-Wißkirchen and Peter Schuster for valuable
guidance, and to Daniel Albert and Caterina Cozzi for their careful readings of
earlier drafts. The work for this note was carried out at the University of
Augsburg, the Max Planck Institute for Mathematics in the Sciences in
Leipzig and the University of Verona.
